
# Import library
```{r}
knitr::opts_chunk$set(eval = FALSE)
rm(list = ls())
library(lubridate)
library(zoo)
library(quantmod)
library(fBasics)
library(tseries)
library(sandwich)
library(lmtest)
library(lattice)
library(xtable)
library(vars)
library(dplyr)
library(gridExtra)
library(corrplot)
library(ggplot2)
library(reshape2)
library(readxl)
library(data.table)
library(rvest)
library(plm)
library(stringr)
library(ggpubr)
library(tidyverse)
library(foreign)
library(stargazer)
library(glmnet)
library(caret)
library(VIM) 
library(tableHTML)
```

### Read Final_Data_Country
```{r}
dat_country.master.master <- read_excel("./Data/Final_Data_Country.xlsx", sheet = "Data")

### Remove countries with population less than 1 million
### dat_country.master.master <- dat_country.master.master[which(dat_country.master.master$population > 1000000),]

dat_country.master.master$Date <- as.Date(dat_country.master.master$Date, origin = "1960-01-01")

Countries <- unique(dat_country.master.master$Country)

Countries

```


### Prepare dataset for panel estimation
```{r}
dat_country <- dat_country.master.master
dat_country$Date <- as.Date(dat_country$Date,"%Y-%m-%d")
dat_country$gdp_per_capita <- dat_country$gdp_per_capita/1000
#reorder
dat_country <- dat_country[order(dat_country$Date),]
dat_country <- dat_country[order(dat_country$Country),]

# dat_country <- dat_country[which(dat_country$Country != "Turkmenistan"),]


dat_country.master <- dat_country %>%
   group_by(Country) %>%
   mutate(Official_New_Mortality = total_deaths_per_million - Lag(total_deaths_per_million,1),
          total_recovery_per_million = total_cases_per_million - total_deaths_per_million,
          Deviation_percent_excess_official = log(cumulative_excess_mortality_per_million) - log(total_deaths_per_million),
          ratio_excess_official = cumulative_excess_mortality_per_million/total_deaths_per_million,
          diff_excess_official = cumulative_excess_mortality_per_million - total_deaths_per_million) 

```

### Impute people vaccinated per hundred and standardize all variables 
```{r}

# Impute total_vaccinations_per_hundred using last observation carried forward
dat_country.master <- dat_country.master[order(dat_country.master$Date),]
dat_country.master <- dat_country.master[order(dat_country.master$Country),]
dat_country.master <- dat_country.master %>%
   dplyr::group_by(Country) %>%
   mutate(total_vaccinations_per_hundred  = ifelse(Date == min(Date) & is.na(total_vaccinations_per_hundred),0,total_vaccinations_per_hundred)) %>%
   mutate(total_vaccinations_per_hundred_imputed = zoo::na.locf(total_vaccinations_per_hundred))

# Impute total_vaccinations_per_hundred using last observation carried forward
dat_country.master <- dat_country.master[order(dat_country.master$Date),]
dat_country.master <- dat_country.master[order(dat_country.master$Country),]
dat_country.master <- dat_country.master %>%
   group_by(Country) %>%
   mutate(people_vaccinated_per_hundred  = ifelse(Date == min(Date) & is.na(people_vaccinated_per_hundred),0,people_vaccinated_per_hundred)) %>%
   mutate(people_vaccinated_per_hundred_imputed = zoo::na.locf(people_vaccinated_per_hundred))

dat_country.master$RuleofLaw <- as.numeric(as.character(dat_country.master$RuleofLaw))
dat_country.master$VoiceandAccountability <- as.numeric(as.character(dat_country.master$VoiceandAccountability))
dat_country.master$GovernmentEffectiveness <- as.numeric(as.character(dat_country.master$GovernmentEffectiveness))
dat_country.master$GINI <- as.numeric(as.character(dat_country.master$GINI))

```

### Quantile samples and summary statistics - official mortality and first year
```{r}

dat_country.cumulative_mortality <- dat_country.master %>%
   dplyr::filter(Date <= "2020-12-31" & !is.na(total_deaths_per_million)) %>%
   dplyr::group_by(Country_Code, Country) %>%
   dplyr::summarise(cumulative_mortality_per_million = last(total_deaths_per_million)) %>%
   arrange(cumulative_mortality_per_million) 

dat_country.cumulative_mortality <- dat_country.cumulative_mortality %>%
   ungroup() %>%
   mutate(Mortality_Ranking = row_number())

library(qpcR)
number_sub_sample <- 4
for (i_quartile in seq(1,number_sub_sample,1)){
   dat.size <- nrow(dat_country.cumulative_mortality)
   if (i_quartile == 1){
      dat_country.quartile <- as.vector(dat_country.cumulative_mortality$Country[which(dat_country.cumulative_mortality$Mortality_Ranking < i_quartile/number_sub_sample*dat.size & dat_country.cumulative_mortality$Mortality_Ranking >= (i_quartile-1)/number_sub_sample*dat.size)])
   } else if (i_quartile != number_sub_sample){
      dat_country.quartile.temp <- as.vector(dat_country.cumulative_mortality$Country[which(dat_country.cumulative_mortality$Mortality_Ranking < i_quartile/number_sub_sample*dat.size & dat_country.cumulative_mortality$Mortality_Ranking >= (i_quartile-1)/number_sub_sample*dat.size)])
      dat_country.quartile <- qpcR:::cbind.na(dat_country.quartile, dat_country.quartile.temp)
      
   } else {
      dat_country.quartile.temp <- as.vector(dat_country.cumulative_mortality$Country[which(dat_country.cumulative_mortality$Mortality_Ranking >= (number_sub_sample-1)/number_sub_sample*dat.size)])
      dat_country.quartile <- qpcR:::cbind.na(dat_country.quartile, dat_country.quartile.temp)
   }
}
dat_country.quartile <- as.data.frame(dat_country.quartile)

colnames(dat_country.quartile) <- seq(1:number_sub_sample)
write_tableHTML(tableHTML(dat_country.quartile,rownames=FALSE, widths = rep(200, number_sub_sample),border = 0), file = paste0("Outputs_Cross Sectional/", Sys.Date(), "_Quartile Sample_first_year_official.htm", sep =""))

### Quartile Sample Summary Statistics

dat_country.summary <- dat_country.master %>%
   ungroup %>%
   dplyr::filter(Date <= "2020-12-31")

dat_country.summary$Mortality_Quartile <- 0
for (i_quartile in c(1:number_sub_sample)){
   if (i_quartile != number_sub_sample){
      dat_country.summary$Mortality_Quartile[which(dat_country.summary$Country %in% dat_country.cumulative_mortality$Country[which(dat_country.cumulative_mortality$Mortality_Ranking < i_quartile/number_sub_sample*dat.size & dat_country.cumulative_mortality$Mortality_Ranking >= (i_quartile-1)/number_sub_sample*dat.size)])] <- i_quartile
   } else{
      dat_country.summary$Mortality_Quartile[which(dat_country.summary$Country %in% dat_country.cumulative_mortality$Country[which(dat_country.cumulative_mortality$Mortality_Ranking >= (i_quartile-1)/number_sub_sample*dat.size)])] <- i_quartile
   }
}

dat_country.summary <- dat_country.summary %>%
   group_by(Country, Country_Code) %>%
   summarise_all(last)

dat_country.quartile.official <- dat_country.summary[,c("Country", "Country_Code", "Mortality_Quartile",
                                                        "population", "population_density", "propurban",  
                                                        "aged_65_older", "gdp_per_capita", 
                                                        "RuleofLaw", "VoiceandAccountability", 
                                                        "GovernmentEffectiveness",
                                                        "total_vaccinations_per_hundred_imputed")]

### Mean
dat_country.quartile.summary <- dat_country.summary[, c("Mortality_Quartile","population", "population_density", "propurban",  
                                                        "aged_65_older", "gdp_per_capita", "RuleofLaw", "VoiceandAccountability", 
                                                        "GovernmentEffectiveness",
                                                        "total_vaccinations_per_hundred_imputed")] %>%
   dplyr::filter(Mortality_Quartile > 0) %>%
   group_by(Mortality_Quartile) %>%
   summarise_all(function (x) mean(x, na.rm = T))
dat_country.quartile.summary$Mortality_Quartile <- NULL
dat_country.quartile.summary <- round(dat_country.quartile.summary, 1)
library(data.table)
dat_country.quartile.summary <- data.table::transpose(dat_country.quartile.summary)
colnames(dat_country.quartile.summary) <- seq(1:number_sub_sample)
rownames(dat_country.quartile.summary) <- c("Population",
                                            "Population Density",
                                            "Urban Population Share",
                                            "Aged 65+ Population Share",
                                            "GDP per Capita",
                                            "Rule of Law",
                                            "Voice and Accountability",
                                            "Government Effectiveness",
                                            "Vaccinations")
write_tableHTML(tableHTML(dat_country.quartile.summary, widths = c(250, rep(150, number_sub_sample)),border = 0), file = paste0("Outputs_Cross Sectional/", Sys.Date(), "_Quartile Sample Summary Statistics_Mean_first_year_official.htm", sep = ""))
### SD
dat_country.quartile.summary <- dat_country.summary[, c("Mortality_Quartile","population", "population_density", "propurban",  
                                                        "aged_65_older","gdp_per_capita", "RuleofLaw", "VoiceandAccountability", 
                                                        "GovernmentEffectiveness",
                                                        "total_vaccinations_per_hundred_imputed")] %>%
   dplyr::filter(Mortality_Quartile > 0) %>%
   group_by(Mortality_Quartile) %>%
   summarise_all(function (x) sd(x, na.rm = T))
dat_country.quartile.summary$Mortality_Quartile <- NULL
dat_country.quartile.summary <- round(dat_country.quartile.summary, 1)
library(data.table)
dat_country.quartile.summary <- data.table::transpose(dat_country.quartile.summary)
colnames(dat_country.quartile.summary) <- seq(1:number_sub_sample)
rownames(dat_country.quartile.summary) <- c("Population",
                                            "Population Density",
                                            "Urban Population Share",
                                            "Aged 65+ Population Share",
                                            "GDP per Capita",
                                            "Rule of Law",
                                            "Voice and Accountability",
                                            "Government Effectiveness",
                                            "Vaccinations")
write_tableHTML(tableHTML(dat_country.quartile.summary, widths = c(250, rep(150, number_sub_sample)),border = 0), file = paste0("Outputs_Cross Sectional/", Sys.Date(), "_Quartile Sample Summary Statistics_SD_first_year_official.htm", sep = ""))
```

### Quantile samples and summary statistics - excess mortality and first year
```{r}

dat_country.cumulative_mortality <- dat_country.master %>%
   dplyr::filter(Date <= "2020-12-31" & !is.na(cumulative_excess_mortality_per_million)) %>%
   dplyr::group_by(Country_Code, Country) %>%
   dplyr::summarise(cumulative_mortality_per_million = last(cumulative_excess_mortality_per_million)) %>%
   arrange(cumulative_mortality_per_million) 

dat_country.cumulative_mortality <- dat_country.cumulative_mortality %>%
   ungroup() %>%
   mutate(Mortality_Ranking = row_number())

library(qpcR)
number_sub_sample <- 4
for (i_quartile in seq(1,number_sub_sample,1)){
   dat.size <- nrow(dat_country.cumulative_mortality)
   if (i_quartile == 1){
      dat_country.quartile <- as.vector(dat_country.cumulative_mortality$Country[which(dat_country.cumulative_mortality$Mortality_Ranking < i_quartile/number_sub_sample*dat.size & dat_country.cumulative_mortality$Mortality_Ranking >= (i_quartile-1)/number_sub_sample*dat.size)])
   } else if (i_quartile != number_sub_sample){
      dat_country.quartile.temp <- as.vector(dat_country.cumulative_mortality$Country[which(dat_country.cumulative_mortality$Mortality_Ranking < i_quartile/number_sub_sample*dat.size & dat_country.cumulative_mortality$Mortality_Ranking >= (i_quartile-1)/number_sub_sample*dat.size)])
      dat_country.quartile <- qpcR:::cbind.na(dat_country.quartile, dat_country.quartile.temp)
      
   } else {
      dat_country.quartile.temp <- as.vector(dat_country.cumulative_mortality$Country[which(dat_country.cumulative_mortality$Mortality_Ranking >= (number_sub_sample-1)/number_sub_sample*dat.size)])
      dat_country.quartile <- qpcR:::cbind.na(dat_country.quartile, dat_country.quartile.temp)
   }
}
dat_country.quartile <- as.data.frame(dat_country.quartile)

colnames(dat_country.quartile) <- seq(1:number_sub_sample)
write_tableHTML(tableHTML(dat_country.quartile,rownames=FALSE, widths = rep(200, number_sub_sample),border = 0), file = paste0("Outputs_Cross Sectional/", Sys.Date(), "_Quartile Sample_first_year_excess.htm", sep =""))

### Quartile Sample Summary Statistics

dat_country.summary <- dat_country.master %>%
   ungroup %>%
   dplyr::filter(Date <= "2020-12-31")

dat_country.summary$Mortality_Quartile <- 0
for (i_quartile in c(1:number_sub_sample)){
   if (i_quartile != number_sub_sample){
      dat_country.summary$Mortality_Quartile[which(dat_country.summary$Country %in% dat_country.cumulative_mortality$Country[which(dat_country.cumulative_mortality$Mortality_Ranking < i_quartile/number_sub_sample*dat.size & dat_country.cumulative_mortality$Mortality_Ranking >= (i_quartile-1)/number_sub_sample*dat.size)])] <- i_quartile
   } else{
      dat_country.summary$Mortality_Quartile[which(dat_country.summary$Country %in% dat_country.cumulative_mortality$Country[which(dat_country.cumulative_mortality$Mortality_Ranking >= (i_quartile-1)/number_sub_sample*dat.size)])] <- i_quartile
   }
}

dat_country.summary <- dat_country.summary %>%
   group_by(Country, Country_Code) %>%
   summarise_all(last)

dat_country.quartile.excess <- dat_country.summary[,c("Country", "Country_Code", "Mortality_Quartile")]

dat_country.quartile.first_year <- merge(dat_country.quartile.official, dat_country.quartile.excess, by = c("Country", "Country_Code"))

### Mean
dat_country.quartile.summary <- dat_country.summary[, c("Mortality_Quartile","population", "population_density", "propurban",  
                                                        "aged_65_older", "gdp_per_capita", "RuleofLaw", "VoiceandAccountability", 
                                                        "GovernmentEffectiveness",
                                                        "total_vaccinations_per_hundred_imputed")] %>%
   dplyr::filter(Mortality_Quartile > 0) %>%
   group_by(Mortality_Quartile) %>%
   summarise_all(function (x) mean(x, na.rm = T))
dat_country.quartile.summary$Mortality_Quartile <- NULL
dat_country.quartile.summary <- round(dat_country.quartile.summary, 1)
library(data.table)
dat_country.quartile.summary <- data.table::transpose(dat_country.quartile.summary)
colnames(dat_country.quartile.summary) <- seq(1:number_sub_sample)
rownames(dat_country.quartile.summary) <- c("Population",
                                            "Population Density",
                                            "Urban Population Share",
                                            "Aged 65+ Population Share",
                                            "GDP per Capita",
                                            "Rule of Law",
                                            "Voice and Accountability",
                                            "Government Effectiveness",
                                            "Vaccinations")
write_tableHTML(tableHTML(dat_country.quartile.summary, widths = c(250, rep(150, number_sub_sample)),border = 0), file = paste0("Outputs_Cross Sectional/", Sys.Date(), "_Quartile Sample Summary Statistics_Mean_first_year_excess.htm", sep = ""))
### SD
dat_country.quartile.summary <- dat_country.summary[, c("Mortality_Quartile","population", "population_density", "propurban",  
                                                        "aged_65_older","gdp_per_capita", "RuleofLaw", "VoiceandAccountability", 
                                                        "GovernmentEffectiveness",
                                                        "total_vaccinations_per_hundred_imputed")] %>%
   dplyr::filter(Mortality_Quartile > 0) %>%
   group_by(Mortality_Quartile) %>%
   summarise_all(function (x) sd(x, na.rm = T))
dat_country.quartile.summary$Mortality_Quartile <- NULL
dat_country.quartile.summary <- round(dat_country.quartile.summary, 1)
library(data.table)
dat_country.quartile.summary <- data.table::transpose(dat_country.quartile.summary)
colnames(dat_country.quartile.summary) <- seq(1:number_sub_sample)
rownames(dat_country.quartile.summary) <- c("Population",
                                            "Population Density",
                                            "Urban Population Share",
                                            "Aged 65+ Population Share",
                                            "GDP per Capita",
                                            "Rule of Law",
                                            "Voice and Accountability",
                                            "Government Effectiveness",
                                            "Vaccinations")
write_tableHTML(tableHTML(dat_country.quartile.summary, widths = c(250, rep(150, number_sub_sample)),border = 0), file = paste0("Outputs_Cross Sectional/", Sys.Date(), "_Quartile Sample Summary Statistics_SD_first_year_excess.htm", sep = ""))
```

### Quantile samples and summary statistics - official mortality and second year
```{r}

dat_country.cumulative_mortality <- dat_country.master %>%
   dplyr::filter(Date <= "2021-12-31" & !is.na(total_deaths_per_million)) %>%
   dplyr::group_by(Country_Code, Country) %>%
   dplyr::summarise(cumulative_mortality_per_million = last(total_deaths_per_million)) %>%
   arrange(cumulative_mortality_per_million) 

dat_country.cumulative_mortality <- dat_country.cumulative_mortality %>%
   ungroup() %>%
   mutate(Mortality_Ranking = row_number())

library(qpcR)
number_sub_sample <- 4
for (i_quartile in seq(1,number_sub_sample,1)){
   dat.size <- nrow(dat_country.cumulative_mortality)
   if (i_quartile == 1){
      dat_country.quartile <- as.vector(dat_country.cumulative_mortality$Country[which(dat_country.cumulative_mortality$Mortality_Ranking < i_quartile/number_sub_sample*dat.size & dat_country.cumulative_mortality$Mortality_Ranking >= (i_quartile-1)/number_sub_sample*dat.size)])
   } else if (i_quartile != number_sub_sample){
      dat_country.quartile.temp <- as.vector(dat_country.cumulative_mortality$Country[which(dat_country.cumulative_mortality$Mortality_Ranking < i_quartile/number_sub_sample*dat.size & dat_country.cumulative_mortality$Mortality_Ranking >= (i_quartile-1)/number_sub_sample*dat.size)])
      dat_country.quartile <- qpcR:::cbind.na(dat_country.quartile, dat_country.quartile.temp)
      
   } else {
      dat_country.quartile.temp <- as.vector(dat_country.cumulative_mortality$Country[which(dat_country.cumulative_mortality$Mortality_Ranking >= (number_sub_sample-1)/number_sub_sample*dat.size)])
      dat_country.quartile <- qpcR:::cbind.na(dat_country.quartile, dat_country.quartile.temp)
   }
}
dat_country.quartile <- as.data.frame(dat_country.quartile)

colnames(dat_country.quartile) <- seq(1:number_sub_sample)
write_tableHTML(tableHTML(dat_country.quartile,rownames=FALSE, widths = rep(200, number_sub_sample),border = 0), file = paste0("Outputs_Cross Sectional/", Sys.Date(), "_Quartile Sample_second_year_official.htm", sep =""))

### Quartile Sample Summary Statistics

dat_country.summary <- dat_country.master %>%
   ungroup %>%
   dplyr::filter(Date <= "2021-12-31")

dat_country.summary$Mortality_Quartile <- 0
for (i_quartile in c(1:number_sub_sample)){
   if (i_quartile != number_sub_sample){
      dat_country.summary$Mortality_Quartile[which(dat_country.summary$Country %in% dat_country.cumulative_mortality$Country[which(dat_country.cumulative_mortality$Mortality_Ranking < i_quartile/number_sub_sample*dat.size & dat_country.cumulative_mortality$Mortality_Ranking >= (i_quartile-1)/number_sub_sample*dat.size)])] <- i_quartile
   } else{
      dat_country.summary$Mortality_Quartile[which(dat_country.summary$Country %in% dat_country.cumulative_mortality$Country[which(dat_country.cumulative_mortality$Mortality_Ranking >= (i_quartile-1)/number_sub_sample*dat.size)])] <- i_quartile
   }
}

dat_country.summary <- dat_country.summary %>%
   group_by(Country, Country_Code) %>%
   summarise_all(last)

dat_country.quartile.official <- dat_country.summary[,c("Country", "Country_Code", "Mortality_Quartile",
                                                        "population", "population_density", "propurban",  
                                                        "aged_65_older", "gdp_per_capita", 
                                                        "RuleofLaw", "VoiceandAccountability", 
                                                        "GovernmentEffectiveness",
                                                        "total_vaccinations_per_hundred_imputed")]

### Mean
dat_country.quartile.summary <- dat_country.summary[, c("Mortality_Quartile","population", "population_density", "propurban",  
                                                        "aged_65_older", "gdp_per_capita", "RuleofLaw", "VoiceandAccountability", 
                                                        "GovernmentEffectiveness",
                                                        "total_vaccinations_per_hundred_imputed")] %>%
   dplyr::filter(Mortality_Quartile > 0) %>%
   group_by(Mortality_Quartile) %>%
   summarise_all(function (x) mean(x, na.rm = T))
dat_country.quartile.summary$Mortality_Quartile <- NULL
dat_country.quartile.summary <- round(dat_country.quartile.summary, 1)
library(data.table)
dat_country.quartile.summary <- data.table::transpose(dat_country.quartile.summary)
colnames(dat_country.quartile.summary) <- seq(1:number_sub_sample)
rownames(dat_country.quartile.summary) <- c("Population",
                                            "Population Density",
                                            "Urban Population Share",
                                            "Aged 65+ Population Share",
                                            "GDP per Capita",
                                            "Rule of Law",
                                            "Voice and Accountability",
                                            "Government Effectiveness",
                                            "Vaccinations")
write_tableHTML(tableHTML(dat_country.quartile.summary, widths = c(250, rep(150, number_sub_sample)),border = 0), file = paste0("Outputs_Cross Sectional/", Sys.Date(), "_Quartile Sample Summary Statistics_Mean_second_year_official.htm", sep = ""))
### SD
dat_country.quartile.summary <- dat_country.summary[, c("Mortality_Quartile","population", "population_density", "propurban",  
                                                        "aged_65_older","gdp_per_capita", "RuleofLaw", "VoiceandAccountability", 
                                                        "GovernmentEffectiveness",
                                                        "total_vaccinations_per_hundred_imputed")] %>%
   dplyr::filter(Mortality_Quartile > 0) %>%
   group_by(Mortality_Quartile) %>%
   summarise_all(function (x) sd(x, na.rm = T))
dat_country.quartile.summary$Mortality_Quartile <- NULL
dat_country.quartile.summary <- round(dat_country.quartile.summary, 1)
library(data.table)
dat_country.quartile.summary <- data.table::transpose(dat_country.quartile.summary)
colnames(dat_country.quartile.summary) <- seq(1:number_sub_sample)
rownames(dat_country.quartile.summary) <- c("Population",
                                            "Population Density",
                                            "Urban Population Share",
                                            "Aged 65+ Population Share",
                                            "GDP per Capita",
                                            "Rule of Law",
                                            "Voice and Accountability",
                                            "Government Effectiveness",
                                            "Vaccinations")
write_tableHTML(tableHTML(dat_country.quartile.summary, widths = c(250, rep(150, number_sub_sample)),border = 0), file = paste0("Outputs_Cross Sectional/", Sys.Date(), "_Quartile Sample Summary Statistics_SD_second_year_official.htm", sep = ""))
```

### Quantile samples and summary statistics - excess mortality and second year
```{r}

dat_country.cumulative_mortality <- dat_country.master %>%
   dplyr::filter(Date <= "2021-12-31" & !is.na(cumulative_excess_mortality_per_million)) %>%
   dplyr::group_by(Country_Code, Country) %>%
   dplyr::summarise(cumulative_mortality_per_million = last(cumulative_excess_mortality_per_million)) %>%
   arrange(cumulative_mortality_per_million) 

dat_country.cumulative_mortality <- dat_country.cumulative_mortality %>%
   ungroup() %>%
   mutate(Mortality_Ranking = row_number())

library(qpcR)
number_sub_sample <- 4
for (i_quartile in seq(1,number_sub_sample,1)){
   dat.size <- nrow(dat_country.cumulative_mortality)
   if (i_quartile == 1){
      dat_country.quartile <- as.vector(dat_country.cumulative_mortality$Country[which(dat_country.cumulative_mortality$Mortality_Ranking < i_quartile/number_sub_sample*dat.size & dat_country.cumulative_mortality$Mortality_Ranking >= (i_quartile-1)/number_sub_sample*dat.size)])
   } else if (i_quartile != number_sub_sample){
      dat_country.quartile.temp <- as.vector(dat_country.cumulative_mortality$Country[which(dat_country.cumulative_mortality$Mortality_Ranking < i_quartile/number_sub_sample*dat.size & dat_country.cumulative_mortality$Mortality_Ranking >= (i_quartile-1)/number_sub_sample*dat.size)])
      dat_country.quartile <- qpcR:::cbind.na(dat_country.quartile, dat_country.quartile.temp)
      
   } else {
      dat_country.quartile.temp <- as.vector(dat_country.cumulative_mortality$Country[which(dat_country.cumulative_mortality$Mortality_Ranking >= (number_sub_sample-1)/number_sub_sample*dat.size)])
      dat_country.quartile <- qpcR:::cbind.na(dat_country.quartile, dat_country.quartile.temp)
   }
}
dat_country.quartile <- as.data.frame(dat_country.quartile)

colnames(dat_country.quartile) <- seq(1:number_sub_sample)
write_tableHTML(tableHTML(dat_country.quartile,rownames=FALSE, widths = rep(200, number_sub_sample),border = 0), file = paste0("Outputs_Cross Sectional/", Sys.Date(), "_Quartile Sample_second_year_excess.htm", sep =""))

### Quartile Sample Summary Statistics

dat_country.summary <- dat_country.master %>%
   ungroup %>%
   dplyr::filter(Date <= "2021-12-31")

dat_country.summary$Mortality_Quartile <- 0
for (i_quartile in c(1:number_sub_sample)){
   if (i_quartile != number_sub_sample){
      dat_country.summary$Mortality_Quartile[which(dat_country.summary$Country %in% dat_country.cumulative_mortality$Country[which(dat_country.cumulative_mortality$Mortality_Ranking < i_quartile/number_sub_sample*dat.size & dat_country.cumulative_mortality$Mortality_Ranking >= (i_quartile-1)/number_sub_sample*dat.size)])] <- i_quartile
   } else{
      dat_country.summary$Mortality_Quartile[which(dat_country.summary$Country %in% dat_country.cumulative_mortality$Country[which(dat_country.cumulative_mortality$Mortality_Ranking >= (i_quartile-1)/number_sub_sample*dat.size)])] <- i_quartile
   }
}

dat_country.summary <- dat_country.summary %>%
   group_by(Country, Country_Code) %>%
   summarise_all(last)

dat_country.quartile.excess <- dat_country.summary[,c("Country", "Country_Code", "Mortality_Quartile")]

dat_country.quartile.second_year <- merge(dat_country.quartile.official, dat_country.quartile.excess, by = c("Country", "Country_Code"))

### Mean
dat_country.quartile.summary <- dat_country.summary[, c("Mortality_Quartile","population", "population_density", "propurban",  
                                                        "aged_65_older", "gdp_per_capita", "RuleofLaw", "VoiceandAccountability", 
                                                        "GovernmentEffectiveness",
                                                        "total_vaccinations_per_hundred_imputed")] %>%
   dplyr::filter(Mortality_Quartile > 0) %>%
   group_by(Mortality_Quartile) %>%
   summarise_all(function (x) mean(x, na.rm = T))
dat_country.quartile.summary$Mortality_Quartile <- NULL
dat_country.quartile.summary <- round(dat_country.quartile.summary, 1)
library(data.table)
dat_country.quartile.summary <- data.table::transpose(dat_country.quartile.summary)
colnames(dat_country.quartile.summary) <- seq(1:number_sub_sample)
rownames(dat_country.quartile.summary) <- c("Population",
                                            "Population Density",
                                            "Urban Population Share",
                                            "Aged 65+ Population Share",
                                            "GDP per Capita",
                                            "Rule of Law",
                                            "Voice and Accountability",
                                            "Government Effectiveness",
                                            "Vaccinatiions")
write_tableHTML(tableHTML(dat_country.quartile.summary, widths = c(250, rep(150, number_sub_sample)),border = 0), file = paste0("Outputs_Cross Sectional/", Sys.Date(), "_Quartile Sample Summary Statistics_Mean_second_year_excess.htm", sep = ""))
### SD
dat_country.quartile.summary <- dat_country.summary[, c("Mortality_Quartile","population", "population_density", "propurban",  
                                                        "aged_65_older","gdp_per_capita", "RuleofLaw", "VoiceandAccountability", 
                                                        "GovernmentEffectiveness",
                                                        "total_vaccinations_per_hundred_imputed")] %>%
   dplyr::filter(Mortality_Quartile > 0) %>%
   group_by(Mortality_Quartile) %>%
   summarise_all(function (x) sd(x, na.rm = T))
dat_country.quartile.summary$Mortality_Quartile <- NULL
dat_country.quartile.summary <- round(dat_country.quartile.summary, 1)
library(data.table)
dat_country.quartile.summary <- data.table::transpose(dat_country.quartile.summary)
colnames(dat_country.quartile.summary) <- seq(1:number_sub_sample)
rownames(dat_country.quartile.summary) <- c("Population",
                                            "Population Density",
                                            "Urban Population Share",
                                            "Aged 65+ Population Share",
                                            "GDP per Capita",
                                            "Rule of Law",
                                            "Voice and Accountability",
                                            "Government Effectiveness",
                                            "Vaccinations")
write_tableHTML(tableHTML(dat_country.quartile.summary, widths = c(250, rep(150, number_sub_sample)),border = 0), file = paste0("Outputs_Cross Sectional/", Sys.Date(), "_Quartile Sample Summary Statistics_SD_second_year_excess.htm", sep = ""))
```

### Save Official vs Excess Quartile
```{r}
dat_country.quartile.first_year <- dat_country.quartile.first_year[,c(1:3, 13, 4:12)]
colnames(dat_country.quartile.first_year)[1:4] <- c("Country", "Country_Code", "Mortality_Quartile_Official", "Mortality_Quartile_Excess")

dat_country.quartile.second_year <- dat_country.quartile.second_year[,c(1:3, 13, 4:12)]
colnames(dat_country.quartile.second_year)[1:4] <- c("Country", "Country_Code", "Mortality_Quartile_Official", "Mortality_Quartile_Excess")
library(openxlsx)
wb_quartile_sample <- createWorkbook()
addWorksheet(wb_quartile_sample, "First_Year")
writeData(wb_quartile_sample, "First_Year", dat_country.quartile.first_year)
addWorksheet(wb_quartile_sample, "Second_Year")
writeData(wb_quartile_sample, "Second_Year", dat_country.quartile.second_year)
saveWorkbook(wb_quartile_sample, "./Outputs_Cross Sectional/Results_Quartile_Official_Excess_updated.xlsx", overwrite = TRUE)
```

### Summary Statistics of Better and Worse Sample
```{r}
dat_doing_better <- dat_country.quartile.second_year[which(dat_country.quartile.second_year$Mortality_Quartile_Excess - dat_country.quartile.second_year$Mortality_Quartile_Official <= -2),]
stargazer(dat_doing_better[,c(5:ncol(dat_doing_better))], type="html",out=file.path("Outputs_Cross Sectional/",paste0(Sys.Date(), "_Table_summary_statistics_doing_better", ".htm", sep = "")))

dat_doing_worse <- dat_country.quartile.second_year[which(dat_country.quartile.second_year$Mortality_Quartile_Excess - dat_country.quartile.second_year$Mortality_Quartile_Official >= 2),]
stargazer(dat_doing_worse[,c(5:ncol(dat_doing_worse))], type="html",out=file.path("Outputs_Cross Sectional/",paste0(Sys.Date(), "_Table_summary_statistics_doing_worse", ".htm", sep = "")))

```

### Cross-sectional regress up to Dec. 31, 2020
```{r}
### Calculate the mean and sd of SI in the first year
dat_country.SI <- dat_country.master %>%
   ungroup() %>%
   dplyr::filter(Date <= "2020-12-28") %>%
   dplyr::group_by(Country) %>%
   dplyr::summarize(SI_mean = mean(StringencyIndex, na.rm = T),
                    SI_sd = stdev(StringencyIndex, na.rm = T))

### Last Value in the first year, i.e., up to Dec. 31, 2020
dat_country.cross_sectional <- dat_country.master %>%
   dplyr::filter(Date == "2020-12-28" & !is.na(total_deaths_per_million)) %>%
   dplyr::filter(cumulative_excess_mortality_per_million > total_deaths_per_million) %>%
   dplyr::filter(cumulative_excess_mortality_per_million > 0)

regmod.cross_sectional.ratio.test <- lm(ratio_excess_official~
                                           gdp_per_capita,
                                        # + RuleofLaw
                                        # + VoiceandAccountability
                                        # + GovernmentEffectiveness,
                                        data=dat_country.cross_sectional, 
                                        na.action="na.exclude")
se.cross_sectional.ratio.test <- coeftest(regmod.cross_sectional.ratio.test, vcov = vcovHC(regmod.cross_sectional.ratio.test, type = "HC1"))

regmod.cross_sectional.ratio <- lm(ratio_excess_official~
                                      gdp_per_capita
                                   + population_density
                                   + propurban
                                   + aged_65_older
                                   + RuleofLaw
                                   + VoiceandAccountability
                                   + GovernmentEffectiveness,
                                   data=dat_country.cross_sectional, 
                                   na.action="na.exclude")
se.cross_sectional.ratio <- coeftest(regmod.cross_sectional.ratio, vcov = vcovHC(regmod.cross_sectional.ratio, type = "HC1"))




```


### 2021 Analysis
```{r}
### Calculate the mean and sd of SI up to Dec. 27 2021
dat_country.SI <- dat_country.master %>%
   dplyr::filter(Date <= "2021-12-27") %>%
   dplyr::group_by(Country) %>%
   dplyr::summarize(SI_mean = mean(StringencyIndex, na.rm = T),
                    SI_sd = stdev(StringencyIndex, na.rm = T))

dat_country.cross_sectional <- dat_country.master %>%
   dplyr::filter(Date == "2021-12-27" & !is.na(total_deaths_per_million))

dat_country.cross_sectional <- dat_country.cross_sectional %>%
   dplyr::filter(cumulative_excess_mortality_per_million > total_deaths_per_million) %>%
   dplyr::filter(cumulative_excess_mortality_per_million > 0) 


regmod.cross_sectional.ratio.second_year.test <- lm(ratio_excess_official~
                                                       gdp_per_capita
                                                    + total_vaccinations_per_hundred_imputed,
                                                    data=dat_country.cross_sectional,
                                                    na.action="na.exclude")

regmod.cross_sectional.ratio.second_year <- lm(ratio_excess_official~
                                                  gdp_per_capita
                                               + population_density
                                               + propurban
                                               + aged_65_older
                                               + RuleofLaw
                                               + VoiceandAccountability
                                               + GovernmentEffectiveness
                                               + total_vaccinations_per_hundred_imputed,
                                               data=dat_country.cross_sectional,
                                               na.action="na.exclude")
se.cross_sectional.ratio.second_year <- coeftest(regmod.cross_sectional.ratio.second_year, vcov = vcovHC(regmod.cross_sectional.ratio.second_year, type = "HC1"))




cov.label <- c(
   "GDP per Capita",
   "Population Density",
   "Urban Population Share",
   "Aged 65+ Population Share",
   "Rule of Law",
   "Voice and Accountability",
   "Government Effectiveness",
   "Total Vaccinations per Hundred Population")


stargazer(digits=4,regmod.cross_sectional.ratio.test,regmod.cross_sectional.ratio, regmod.cross_sectional.ratio.second_year.test,  regmod.cross_sectional.ratio.second_year, type="html",out=file.path("Outputs_Cross Sectional/",paste0(Sys.Date(), "_Table_baseline_cs_output_first_and_second_year_combined_test", ".htm", sep = "")),
          column.labels=c("As of 12/28/2020", "As of 12/27/2021"),
          column.separate = c(2,2),
          align = TRUE,
          dep.var.labels = "E/O",
          dep.var.labels.include = TRUE,
          covariate.labels=cov.label, 
          df = FALSE,omit.stat="adj.rsq",notes = c("*,**,*** correspond to 10%, 5% and 1% significance, respectively."),notes.append=F,notes.align ="l",title=paste("Cross Sectional Regression"),table.layout = "-ldmc#-t=sa-n")

```

###{r}
```{r}
library(xtable)
correlation_matrix <- as.data.frame(cor(as.matrix(dat_country.cross_sectional[, c("total_vaccinations_per_hundred_imputed",
                                                                                  "population_density", 
                                                                                  "propurban",
                                                                                  "aged_65_older",
                                                                                  "gdp_per_capita",
                                                                                  "RuleofLaw",
                                                                                  "VoiceandAccountability",
                                                                                  "GovernmentEffectiveness")]), use = "complete.obs"))
write_excel_csv(correlation_matrix, "./Outputs_Cross Sectional/Correlation_Matrix.csv")
```

